Random Fibonacci Anyons Simulable via Covariant Action of Mapping Class Group

### 2014-09-02 about.tex
diagrams

\documentclass[12pt,a4paper]{article}
%\documentclass[11pt, twocolumn]{article}

@@

Technical contribution: 
(1) discretization of curve diagrams,
(2) classification theorem
(3) simulation

@@

@@

\begin{center}
\includegraphics[width=0.4\textwidth]{discrete-curve.eps}
\end{center}

@@

Poisson process, pair creation $t_{\mathrm{sim}}$

PICTURE

Extraction of syndrome

PICTURE

Multi-round
Clustering of charges, \cite{Brell13} \cite{Bravyi13}

Fail on big braid

>>>>

\documentclass[11pt,a4paper]{article}
%\documentclass[11pt, twocolumn]{article}

@@

Technical contribution: 
(1) classification theorem
(2) discretization of curve diagrams
(3) simulation

@@

the dimensionality of the state space
of anyons grows as $d^n$.
For fibonacci anyons $d\simeq 1.6$ and
it is known that braiding generates a dense
set of unitaries on the state space, so we
only expect to be able to simulate for small $n.$

@@

\begin{center}
\includegraphics[width=0.3\textwidth]{discrete-curve.eps}
\end{center}

@@

\begin{center}
(i)
\includegraphics[width=0.26\textwidth]{pair-create.eps}
\hskip 10pt
(ii)
\includegraphics[width=0.26\textwidth]{syndrome-1.eps}
\hskip 10pt
(iii)
\includegraphics[width=0.26\textwidth]{syndrome-2.eps}
\end{center}

We Maintain a collection of disjoint curves.

(i) Poisson process, pair creation $t_{\mathrm{sim}}$.

(ii) join fusion trees (curves)
that participate in the same site (tile).
(iii) measure charge on each site and leave result on
one of the strands.
These charge measurements give the initial syndrome for the
error correction procedure.

Multi-round, clustering of charges, \cite{Brell13} \cite{Bravyi13}

Torus:
Fail on big braid
